Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Add wire diagrams.
Tweak protocol figure.

@@

\begin{figure}
% Use a child's garden--like figure of the HTTP protocol here.
\tiny
\usefont{U}{cmtt}{m}{n}%
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 517

\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f\xf5\xbb
...
\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 739

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2\x78\x7d
...
\end{verbatim}
\end{quote}
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 75\r\n

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25\x72\x1e
...
\end{verbatim}
\end{quote}
\caption{
The meek protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02...}
is the beginning of a TLS handshake).
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-ID headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

>>>>

% https://tex.stackexchange.com/questions/113338/use-sans-serif-in-a-verbatim-environment/113339#113339
\makeatletter
\def\verbatim@font{\usefont{U}{cmtt}{m}{n}}
\makeatother

@@

\begin{figure}
\scriptsize
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 517

\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f...
\end{verbatim}
\smallskip
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 739

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2...
\end{verbatim}
\end{quote}
\smallskip
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

\end{verbatim}
\smallskip
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 75

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-ID headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.40\linewidth}
\includegraphics[width=\linewidth]{wire-sequential}
\caption{Sequential}
\label{fig:wire-sequential}
\end{subfigure}
\qquad
\begin{subfigure}[t]{0.40\linewidth}
\includegraphics[width=\linewidth]{wire-parallel}
\caption{Parallel}
\label{fig:wire-parallel}
\end{subfigure}

\caption{
The nature of potential performance gain
from sending fronted requests in parallel.
}
\label{fig:wire}
\end{figure}
